---
title: "R recap"
author: "Your Name Here"
date: '27th April'
output: pdf_document
---


## Getting started

First load the wakefield package

```{r}
library(wakefield)
```

Now run this function

```{r}
random_patients <- function(n) {
  as.data.frame(r_data_frame(
    n,
    id,
    name,
    race,
    sex,
    smokes,
    height,
    birth(random = TRUE, x = NULL, start = Sys.Date() - 365 * 45, k = 365*2,by = "1 days"),
    state,
    pet,
    grade_level(x=1:3),
    died,    
    normal(name="Count"),
    date_stamp)
  )
}

```



```{r}
patients <- random_patients(10)
```

```{r}
View(patients)
```


******

## Q. What are the dimensions of the data frame?

## Q. What columns are available?

*** HINT: see the `dim`, `ncol`, `nrow` and `colnames` functions
 
******


```{r }
```

******
## Q. Can you think of two ways to access the Names of the patients?
## Q. What type of object is returned?

******
```{r}
```



## Subsetting


******
## Q. Make sure you can understand the behaviour of the following commands
******

```{r}
patients[1,2]
patients[2,1]
patients[c(1,2,3),1]
patients[c(1,2,3),c(1,2,3)]
```


******
## Q. Make sure you can understand the behaviour of the following commands
******


```{r}
patients[1,]
patients[,1]
patients[,c(1,2)]
```



******
## Q. Can you create a data frame of dog owners?

******


```{r}

```


******
## Q. Can you create a data frame of deceased patients with a 'count' < 0

******

```{r}

```

******
## Q. Create a data frame where the patients are arranged in decreasing height order

******

## Simple plotting



```{r}
hist(patients$Height)
```


```{r}
plot(patients$Height,patients$Count)
```


```{r}
barplot(table(patients$Race))
```

```{r}
barplot(table(patients$Pet))
```


```{r}
boxplot(patients$Count ~ patients$Died)
```


```{r}
plot(patients$Height,patients$Count,pch=16,
     col="red",xlab="Height",
     ylab="Count")
```


```{r}
boxplot(patients$Count ~ patients$Died,col=c("red","yellow"))
```

******
## Make the following plots
## 1. Histogram of the Count variable
## 2. Barplot of the frequency of pet ownership
## 3. Boxplot of Height according to smoker / non-smoker
## ...anything else that takes your fancy

******

```{r}
png("myLittlePlot.png")
barplot(table(patients$Pet))
dev.off()
```
